The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-27 dit-paper_ieee.tex
hotfix

		Algorithm~\ref{alg:algoCRP} finds one DIT given one combination of $a_i$
		values. However using it in practice is very inefficient as there are
		exponentially many different combinations of $a_i$ values in the number of
		tasks (the cartesian product of all the $A_i$ sets), and resolving
		exponentially many CRP instances is prohibitively slow.
		A faster method for finding the FPDIT consists in merging all these CRP
		instances into one problem (finding all DITs), which can be solved faster by
		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
		results are shared between instances. The first part consisting in splitting
		all constraints into sets of constraints with prime power moduli is slightly
		different. We define for each task $\tau_i$ and $a_j \in A_i$ :
		$C_{ij}$ is the set of constraints resulting from the factorisation of $t_d
		\equiv a_j+O_i \; (mod \; n_i)$ of the form $t_d \equiv x_c
		\; (mod \; p_c)$ if named $c$. We define $C = \cup\limits_{\tau_i \in \tau,
		a_j \in A_i}{C_{ij}}$, $P$ the set of all $p_c$ values appearing in
		constraints of $C$ and $C_{p}$ the subset of $C$ containing all constraints
		$c$ with $p_c = p$.

>>>>

		Algorithm~\ref{alg:algoCRP} finds one DIT given one combination of $a_i$
		values. However using it in practice is very inefficient as there are
		exponentially many different combinations of $a_i$ values in the number of
		tasks (the cartesian product of all the $A_i$ sets), and resolving
		exponentially many CRP instances is prohibitively slow.
		A faster method for finding the FPDIT consists in merging all these CRP
		instances into one problem (finding all DITs), which can be solved faster by
		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
		results are shared between instances. The first part consisting in splitting
		all constraints into sets of constraints with prime power moduli is slightly
		different. We define for each task $\tau_i$ and $a_j \in A_i$ :
		$C_{ij}$ is the set of constraints resulting from the factorisation of $t_d
		\equiv a_j+O_i \; (mod \; n_i)$ of the form $t_d \equiv x_c
		\; (mod \; p_c)$ if named $c$. We define $C = \bigcup\limits_{\tau_i \in \tau,
		a_j \in A_i}{C_{ij}}$, $P$ the set of all $p_c$ values appearing in
		constraints of $C$ and $C_{p}$ the subset of $C$ containing all constraints
		$c$ with $p_c = p$.
